---
title: "Course Description Trigrams"
output: html_notebook
---



```{r}
library(dplyr)
library(tidytext)
library(tidyr)
library(readr)
```
#Pulling in course data from downloaded file and ensuring UTF-8 Encoding
```{r}
Sys.setlocale(locale = "en_BE.UTF-8")
df <- read_csv("2013-2024coursedata.csv", col_types = cols(.default = "c"))

```
#Creating desired subset by discipline
```{r}
#entire department, in this case sociology
deponly <- subset(df, Department =="SO")
depdesc <- select(deponly,Description, Year)
#can save a file for that entire discipline for further analysis if needed/ write.csv(soconly, "soconly.csv", fileEncoding = "UTF-8")
```
#Making the trigrams
```{r}
deptrigrams <- depdesc %>%
  unnest_tokens(trigram, Description, token="ngrams", n=3)
```
#Filtering stopwords
```{r}
#the custom stop word list will change for each domain, an external .txt file can be saved and imported with read.table
customstopwords <- c("prerequisite", "consent", "instructor", "prerequisites", "hour", "hours", "topic", "topics", "including", "credit", "credits", "e.g.","requisites", "e.g", "so", "hrs","completes", "include", "includes", "i.e", "offered", "approval", "senior", "enrollment", "practical","sociology", "basic", "qualitative")
#separating the trigrams to one word per cell allows the stop words to be edited out and the count the number of occurrences
trigrams_separated <- deptrigrams %>%
  separate(trigram, c("word1","word2","word3"), sep = " ")
trigrams_filtered <- trigrams_separated %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word) %>%
  filter(!word3 %in% stop_words$word) %>%
  filter(!word1 %in% customstopwords) %>%
  filter(!word2 %in% customstopwords) %>%
  filter(!word3 %in% customstopwords)
```
#Frequency count of trigrams overall, it is very important to rename the file in the final step so as not to overwrite previous output
```{r}
trigram_counts <- trigrams_filtered %>%
  count(word1, word2, word3, sort = TRUE) %>% unite(trigram, word1, word2, word3, sep = " ")
#rename the file here for each department
write.csv(trigram_counts, file="deptrigramcounts.csv", fileEncoding = "UTF-8")
```
#Uniting the trigrams here does not include count but does include each instance by year, renaming the file is also important
```{r}
trigrams_united <-trigrams_filtered %>%
  unite(trigram, word1, word2, word3, sep = " ")
write.csv(trigrams_united, file = "deptrigramsall.csv", fileEncoding = "UTF-8")
```
#Generating wordclouds
```{r}
library(wordcloud2)
wc <- data.frame(trigram_counts$trigram, trigram_counts$n)
wordcloud2(data = wc,color = "random-light", backgroundColor = "#FFFFFF", size = 1, shape = "triangle")
#The wordcloud2 library has several different options for shapes, colors, and frequency cut off
```


